The impact of cosmic variance on simulating weak lensing surveys

### 2014-12-01 Writeup/paper_v3.tex
more on training dataset sizes

It is important to keep in mind the nature of COSMOS with respect to
other possible {\em HST} training samples.  COSMOS represents the
largest contiguous field surveyed by the {\em HST}, with the sizes of
other major {\em HST} fields such as GOODS and AEGIS lagging by at least a
\rachelnew{factor of 9 (for AEGIS, and more for GOODS).  The GEMS field
  comes the closest to that of COSMOS, but is still a factor of 6
  smaller and may be less useful for determination of colour gradients
  given that one of the bands, F850LP, is relatively shallow.}.
Hence, if cosmic variance due to structures along 
the line-of-sight in COSMOS are problematic for its use as a training
sample for weak lensing simulations, studies that use even smaller
area training samples are even more prone to errors, with the UDF
serving as an extreme case.  If the size of the {\em HST} survey is
small enough, there is no reason {\em a priori} to suppose that the
galaxy population is typical even when using all galaxies along the
line of sight, without any division into redshift bins.  Of course,
future surveys are unlikely to pick just a single survey to serve as
the basis for their image simulation training sample, but rather
will combine as many as possible.  Combining multiple surveys will
reduce the cosmic variance and therefore the significance of the
effects discussed in this work.
However, as COSMOS is significantly larger than other \emph{HST} surveys, combining COSMOS with smaller fields is unlikely to ameliorate this effect.
Thus, it will be important to carefully choose the size of redshift slices used to
derive properties of the galaxy population so as to be minimally
affected by this issue.

>>>>

It is important to keep in mind the nature of COSMOS with respect to
other possible {\em HST} training samples.  COSMOS represents the
largest contiguous field surveyed by the {\em HST}, with the sizes of
other major {\em HST} fields such as GOODS and AEGIS lagging by at least a
\rachelnew{factor of 9 (for AEGIS, and more for GOODS).  Combinations
  of CANDELS with existing datasets may ultimately be as large as
  $1/6$ the COSMOS area.}.
Hence, if cosmic variance due to structures along 
the line-of-sight in COSMOS are problematic for its use as a training
sample for weak lensing simulations, studies that use even smaller
area training samples are even more prone to errors, with the UDF
serving as an extreme case.  If the size of the {\em HST} survey is
small enough, there is no reason {\em a priori} to suppose that the
galaxy population is typical even when using all galaxies along the
line of sight, without any division into redshift bins.  Of course,
future surveys are unlikely to pick just a single survey to serve as
the basis for their image simulation training sample, but rather
will combine as many as possible.  Combining multiple surveys will
reduce the cosmic variance and therefore the significance of the
effects discussed in this work.
However, as COSMOS is significantly larger than other \emph{HST} surveys, combining COSMOS with smaller fields is unlikely to ameliorate this effect.
Thus, it will be important to carefully choose the size of redshift slices used to
derive properties of the galaxy population so as to be minimally
affected by this issue.
